%% experience.tex

\section{Experience}

\cventry{2025--present}
  {Student Research Assistant (HiWi)}
  {Manufacturing Technology Institute, RWTH Aachen}
  {Aachen, Germany}
  {}
  {
    \begin{itemize}
      \item Developed a modular Python framework to automate and orchestrate Finite Element simulations in Abaqus.
      \item Implemented the Contour Method to predict distortions and residual stresses in titanium components.
      \item Designed an object-oriented architecture to manage geometry definition, batch simulation execution, and automatic post-processing.
      \item Created routines to convert native results (ODB) to external visualization formats, ensuring reproducibility and integration with experimental data.
    \end{itemize}
  }

\cventry{2024}
  {Engineering Intern}
  {Loopzero}
  {Brazil}
  {}
  {
    \begin{itemize}
      \item Modeled filling and solidification of aluminum cast parts using Magmasoft to predict defects and optimize molds.
      \item Identified bottlenecks in engineering documentation and developed custom automation routines.
      \item Automated data extraction from simulations to generate technical reports in PowerPoint, drastically reducing time on repetitive tasks.
      \item Standardized result presentation to allow greater focus on critical analysis of casting processes.
    \end{itemize}
  }

\cventry{2023}
  {Research Scholarship -- Vortex-Induced Vibrations}
  {UDESC -- Santa Catarina State University}
  {Joinville, Brazil}
  {}
  {
    \begin{itemize}
      \item Investigated the excitation of the first torsional vibration mode in cantilever structures focusing on VIV.
      \item Modeled laminated composites using ANSYS ACP to analyze the sensitivity of dynamic response to fiber orientations and stacking sequences.
      \item Implemented two-way FSI simulations coupling Fluent with ANSYS Transient Structural.
    \end{itemize}
  }

\cventry{2022}
  {Research Scholarship -- Additive Manufacturing \& Tribology}
  {UDESC -- Santa Catarina State University}
  {Joinville, Brazil}
  {}
  {
    \begin{itemize}
      \item Collaborated on the Rota 2030 program focusing on additive manufacturing of molds for aluminum injection with internal cooling channels.
      \item Conducted tribological characterization tests to evaluate abrasive wear resistance of candidate steel alloys via pin-on-disc tribometer.
      \item Executed the complete metallographic sample preparation cycle.
    \end{itemize}
  }

\cventry{2020--2022}
  {Teaching Assistant -- Mathematics}
  {UDESC -- Santa Catarina State University}
  {Joinville, Brazil}
  {}
  {
    \begin{itemize}
      \item Supported undergraduate students in fundamental mathematics concepts and problem-solving skills for two years.
    \end{itemize}
  }

\cventry{2019}
  {Trainee -- Suspension Subsystem}
  {Velociraptor Baja SAE Team}
  {Joinville, Brazil}
  {}
  {
    \begin{itemize}
      \item Redesigned suspension geometry to increase directional stability in high-speed curves.
      \item Utilized MSC ADAMS to simulate kinematic behavior and reaction forces.
      \item Conducted FEA in ANSYS to ensure component integrity under impact and fatigue loads.
    \end{itemize}
  }